\documentclass[a4paper,12pt]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{setspace}
\doublespacing
\title{Estimation}
\author{}
\date{}

\begin{document}
\maketitle

\section{Rounding}
\subsection{Rounding Up}
Rounding up is the process of estimating a number to its nearstest higher value.
\subsubsection{Example}
Round up each of the following to the required accuracy.
\[21.16\text{ (1 dp)}\quad7894\text{ (tens digit)}\quad7894\text{ (hundreds digit)}\]

\newpage

\subsection{Rounding Down}
Rounding down is the process of estimating a number to its nearstest lower value.
\subsubsection{Example}
Round down each of the following to the required accuracy.
\[21.16\text{ (1 dp)}\quad7894\text{ (tens digit)}\quad7894\text{ (hundreds digit)}\]
\subsection{Rounding Off}
Rounding off is the process of estimating a number to its nearstest greater value. Use the rule of round down below 5 and round up above or equal 5.
\subsubsection{Example}
Round off each of the following to the required accuracy.
\[21.16\text{ (1 dp)}\quad7894\text{ (tens digit)}\quad7894\text{ (hundreds digit)}\]

\newpage

\section{Significant Figures}
Significant figures show the precision of measurements. The higher the number of significant figures a measurement has, the more precise the measurement is.
\subsection{Rules}
\begin{itemize}
	\item 1.23 has 3 significant figures (All the digits give us information on how accurate the measurement is)
	\item 0.123 has 3 significant figures (The first zero only tell us the size, and not the accuracy of the measurement)
	\item 0.1230 has 4 significant figures (The last zero tells us that this number has been rounded off, so it is significant)
	\item 0.10023 has 5 significant figures (All the zeros between the significant figures are significant)
	\item 10.0 has 3 significant figures (The zero between the significant figures is significant too)
	\item 10 has either 2 significant figures or 1 significant figure (Depending on the question)
\end{itemize}
\subsection{Example}
Round off each of the following to the required accuracy.
\[21.16\text{ (1 sf)}\quad7894\text{ (2 sf)}\quad7894\text{ (3 sf)}\]
\end{document}
